### 2020-04-19 serial.tex
Finish the ¶
minor changes

\jd{An alternative approach that I'm pretty sure produces a slightly different answer. I'm going to write it in a mixed notation:}
The number of SIs that go from $\delta_1$ to $\delta_2$ is an integral over all of the possibilities for the infection times.
\begin{equation}
	N(\delta_1, \delta_2) = \int \int d\alpha_1 d\alpha_2
	i(\alpha_1) h(\delta_1-\alpha_1, \alpha_2-\alpha_1)
	S(\alpha_2)\theta(\delta_2-\alpha_2)
\end{equation}
To get the forward SI, we substitute $\delta_2 = \delta_1+\tau$ and normalize. And so on.
Likewise, we can define the backward serial interval distribution for a secondary cohort $\ell$ (\fref{diagram}B).
Given that an infectee became symptomatic at time $\ell$, we have to first go backward in time by asking when the infectee became infected and when the infector became infected; 
then, we have to go forward in time by asking when the infector became symptomatic.
In this case, $x_1$ and $\sigma$ represent the backward incubation period and generation interval, respectively, and $x_0$ represents the forward incubation period.
Therefore, the backward serial interval distribution of a secondary cohort $\ell$ can be written as follows
\begin{equation}
\begin{aligned}
b_\ell(\tau) &\propto j(\ell) f_{\ell}(\tau)\\
&\propto \int_0^\infty \mathcal R_c (\ell - x_0) i(\ell-x_0) k(x_0) f_{\ell}(\tau) \mathrm{d} x_0
\end{aligned}
\end{equation}
where $j$ represents the incidence of symptomatic infectors.

@@

Here, we use a renewal equation to model the spread of disease in a population \citep{heesterbeek1996concept, diekmann2000mathematical, roberts2004modelling, aldis2005integral, roberts2007model, champredon2018equivalence}.
Ignoring the dynamics of births and deaths, changes in the proportion of susceptible individuals $S(t)$ and incidence of infection $i(t)$ can be written as:
\begin{equation}
\begin{aligned}
\frac{\mathrm{d}S}{\mathrm{d}t} &= - i(t)\\
i(t) &= \mathcal R_0 S(t) \int_0^\infty i(t-\tau) g(\tau) \mathrm{d}\tau,
\end{aligned}
\label{eq:renewal}
\end{equation}
where $\mathcal R_0$ is the basic reproduction number, and $g(\tau)$ is the intrinsic generation-interval distribution (i.e., the forward generation-interval distribution of a primary case in a fully susceptible population; \cite{champredon2015intrinsic}).
Then, the forward generation-interval for a primary cohort $\ell$ follows \citep{champredon2015intrinsic}:
\begin{equation}
g_\ell (\tau) \propto g(\tau) S(\ell + \tau),
\end{equation}
which allows us to separate the joint probability distribution $h_\ell$ of the forward incubation period and the forward generation-interval distribution as a product of the proportion of susceptible individuals $S$ and the joint probability distribution $h$ of the forward incubation period and the intrinsic generation intervals:
\begin{equation}
h_\ell (x_0, \tau) \propto h(x_0, \tau) S(\ell + \tau),
\end{equation}
which satisfies the following:
\begin{equation}
g(\tau) = \int_0^\infty h(x_0, \tau) \mathrm{d}x_0.
\end{equation}
Finally, the cohort reproduction for this model is defined as follows:
\begin{equation}
\mathcal R_c(t) = \mathcal R_0 \int_0^\infty g(\tau) S(t+\tau) \mathrm{d} \tau.
\end{equation}

>>>>

\jd{An alternative approach that I'm pretty sure produces a slightly different answer. I'm going to write it in a mixed notation:}
The number of SIs that go from $\delta_1$ to $\delta_2$ is an integral over all of the possibilities for the infection times.
\begin{equation}
	N(\delta_1, \delta_2) = \int \int d\alpha_1 d\alpha_2
	i(\alpha_1) h(\delta_1-\alpha_1, \alpha_2-\alpha_1)
	S(\alpha_2)\theta(\delta_2-\alpha_2)
\end{equation}
To get the forward SI, we substitute $\delta_2 = \delta_1+\tau$ and normalize. And a similar trick (from the same starting point) to get the backward SI.

Likewise, we can define the backward serial interval distribution for a secondary cohort $\ell$ (\fref{diagram}B).
Given that an infectee became symptomatic at time $\ell$, we have to first go backward in time by asking when the infectee became infected and when the infector became infected; 
then, we have to go forward in time by asking when the infector became symptomatic.
In this case, $x_1$ and $\sigma$ represent the backward incubation period and generation interval, respectively, and $x_0$ represents the forward incubation period.
Therefore, the backward serial interval distribution of a secondary cohort $\ell$ can be written as follows
\begin{equation}
\begin{aligned}
b_\ell(\tau) &\propto j(\ell) f_{\ell}(\tau)\\
&\propto \int_0^\infty \mathcal R_c (\ell - x_0) i(\ell-x_0) k(x_0) f_{\ell}(\tau) \mathrm{d} x_0
\end{aligned}
\end{equation}
where $j$ represents the incidence of symptomatic infectors.

@@

We validate the theory by applying it to a specific example of an epidemic model. 
We model disease spread with a renewal-equation model \citep{heesterbeek1996concept, diekmann2000mathematical, roberts2004modelling, aldis2005integral, roberts2007model, champredon2018equivalence}.
Ignoring births and deaths, changes in the proportion of susceptible individuals $S(t)$ and incidence of infection $i(t)$ can be written as:
\begin{equation}
\begin{aligned}
\frac{\mathrm{d}S}{\mathrm{d}t} &= - i(t)\\
i(t) &= \mathcal R_0 S(t) \int_0^\infty i(t-\tau) g(\tau) \mathrm{d}\tau,
\end{aligned}
\label{eq:renewal}
\end{equation}
where $\mathcal R_0$ is the basic reproduction number, and $g(\tau)$ is the intrinsic generation-interval distribution (i.e., the forward generation-interval distribution of a primary case in a fully susceptible population; \cite{champredon2015intrinsic}).
Then, the forward generation-interval for a primary cohort $\ell$ follows \citep{champredon2015intrinsic}:
\begin{equation}
g_\ell (\tau) \propto g(\tau) S(\ell + \tau),
\end{equation}
which allows us to separate the joint probability distribution $h_\ell$ of the forward incubation period and the forward generation-interval distribution as a product of the proportion of susceptible individuals $S$ and the joint probability distribution $h$ of the forward incubation period and the intrinsic generation intervals:
\begin{equation}
h_\ell (x_0, \tau) \propto h(x_0, \tau) S(\ell + \tau),
\end{equation}
which satisfies the following:
\begin{equation}
g(\tau) = \int_0^\infty h(x_0, \tau) \mathrm{d}x_0.
\end{equation}
Finally, the cohort reproduction for this model is defined as follows:
\begin{equation}
\mathcal R_c(t) = \mathcal R_0 \int_0^\infty g(\tau) S(t+\tau) \mathrm{d} \tau.
\end{equation}
